---
title: "Case 1"
author: "John Yan, Hannah Kosinovsky, David Nguyen"
date: "October 15, 2018"
output: html_document
---

## Data Overview

This study contains a data analysis of two datasets Beers.csv and Breweries.csv. The Beers dataset contains a list of 2410 US craft beers and Breweries dataset contains 558 US breweries.

```{r setup}
#install.packages("ggplot2")

beers = read.csv(file="beers.csv", header = TRUE)
head(beers)
str(beers)

breweries = read.csv(file="Breweries.csv", header = TRUE)
head(breweries)
str(breweries)

names(breweries)[1] = "Brewery_id"
names(breweries)
head(breweries)
str(breweries)

```

## Question 1

How many breweries are present in each state?

```{r}
library(data.table) ## >= v1.9.6
setDT(breweries)[, .(count = uniqueN(Brewery_id)), by = State]
```


## Question 2

Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.

```{r}
beer_brews = merge(beers, breweries, by = "Brewery_id", all = FALSE)
head(beer_brews, 6)
tail(beer_brews, 6)
```

## Question 3

Report the number of NA's in each column.

```{r}
colSums(is.na(beer_brews))
```

## Question 4

Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
Need to ignore nas for median
Plot the median ABV and IBU using GGplot
```{r}

df1 = setDT(beer_brews)[,list(Mean=mean(ABV, na.rm = TRUE), Max=max(ABV, na.rm = TRUE), Min=min(ABV, na.rm = TRUE), Median=as.numeric(median(ABV, na.rm = TRUE)), Std=sd(ABV, na.rm = TRUE)), by=State]

AK = beer_brews[beer_brews$State == " AK",]
median(AK$ABV, na.rm = TRUE)

df = setDT(beer_brews)[,list(Mean=mean(IBU, na.rm = TRUE), Max=max(IBU), Min=min(IBU), Median=as.numeric(median(IBU, na.rm = TRUE)), Std=sd(IBU, na.rm = TRUE)), by=State]

library(ggplot2)
ggplot(data=df, aes(x=State, y=Median, fill=State)) +
  geom_bar(stat="identity", show.legend=FALSE) + labs(x = "State", y = "Median of IBU", 
                                                      title = "Median IBU per state") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(data=df1, aes(x=State, y=Median, fill=State)) +
  geom_bar(stat="identity", show.legend=FALSE) + labs(x = "State", y = "Median of ABV", 
                                                      title = "Median ABV per state") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```
## Question 5

Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

```{r}
beer_brews[beer_brews$IBU == max(beer_brews$IBU, na.rm = TRUE),]

beer_brews[beer_brews$ABV == max(beer_brews$ABV, na.rm = TRUE),]

```

## Question 6
Summary statistics for the ABV variable

```{r}
setDT(beer_brews)[,list(Mean=mean(ABV, na.rm = TRUE), Max=max(ABV, na.rm = TRUE), Min=min(ABV, na.rm = TRUE), Median=as.numeric(median(ABV, na.rm = TRUE)), Std=sd(ABV, na.rm = TRUE))]

mean(beer_brews$ABV, na.rm = TRUE)

```

## Question 7

Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.
Calculate the correlation coefficient

```{r}
ggplot(beer_brews, aes(x=ABV, y=IBU)) + 
  labs(x = "ABV", y = "IBU", title = "Scatterplot of bitterness versus alcoholic content") + 
  geom_point(shape=1) +    
  geom_smooth(method=lm)

cor(beer_brews$ABV, beer_brews$IBU)
```